---
title: "p8105_hw6_wl2829"
author: "Wentong"
date: "12/3/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

Import and tidy data

```{r}
birthweight_df =
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = factor(recode(babysex, `1` = "male", `2` = "female")),
    frace = factor(recode(frace, `1` = "White", `2` = "Black", `3` = "Asian",
                          `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown")),
    mrace = factor(recode(mrace, `1` = "White", `2` = "Black", `3` = "Asian",
                          `4` = "Puerto Rican", `8` = "Other"))
  ) ## recode the data
```

Propose a regression model for birthweight. 

```{r}
lm_mod1 = lm(bwt ~ mheight, data = birthweight_df)
```

```{r}
birthweight_df %>% 
  select(bwt, mheight) %>% 
  add_predictions(lm_mod1) %>% 
  add_residuals(lm_mod1) %>% 
  ggplot(aes(x = mheight, y = resid)) +
  geom_violin()
```

Compare models

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    lm_mod1 = map(train, ~lm(bwt ~ mheight, data = .x)),
    lm_mod2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    lm_mod3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(
   rmse1 = map2_dbl(lm_mod1, test, ~rmse(model = .x, data = .y)),
   rmse2 = map2_dbl(lm_mod2, test, ~rmse(model = .x, data = .y)),
   rmse3 = map2_dbl(lm_mod3, test, ~rmse(model = .x, data = .y)))
```

Visualization of the models

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

The smaller the value of rmse, the better the model, so from the plot, we can conclude that `lm_mod3` is the best model. 

## Problem 2

Import data.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Build `boot_sample` function.

```{r}
boot_sample = function(df) {
  
  sample_frac(df, replace = TRUE)
  
}
```

Bootstrapping. Create a list column

```{r}
boot_straps = 
  tibble(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )

```

### r squared estimate

```{r}
bootstrap_results1 = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>% 
  select(strap_number, results) %>% 
  unnest(results)

bootstrap_results1 %>% ## make a plot
  ggplot(aes(x = r.squared)) +
  geom_density()
```

The shape of the distribution of estimates can be used to evaluate the performance of the estimator. The bootstrap distribution is centered at approximately 0.91 and the shape has a heavy tail extending to low values.

Confidence Interval
```{r}
CI = c(quantile(bootstrap_results1$r.squared, 0.025), quantile(bootstrap_results1$r.squared, 0.975))
```

The 95% confidence interval is (`r CI`).

### Beta estimate

```{r}
bootstrap_results2 = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(names_from = term,
              values_from = estimate) %>% 
  mutate(log_beta = log(`(Intercept)` * tmin))

bootstrap_results2 %>% 
  ggplot(aes(x = log_beta)) + 
  geom_density()
```

The distribution is centered at approximately 2.02 and the shape of distribution look similar to normal distribution.

Confidence Interval

```{r}
CI = c(quantile(bootstrap_results2$log_beta, 0.025), quantile(bootstrap_results2$log_beta, 0.975))
```

The 95% confidence interval is (`r CI`).